---
title: "Machine Learning for Text Analysis Workshop"
author:   
  - name: "**Content Creator: Camille Johnston**"
  - name: "**Content Editors: Steven Martinez, Katie Jobson, Billy Mitchell, and Helen Schmidt**"
date: "2024-07-10"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    df_print: paged
    css: !expr here::here("_misc/style_bootcamp.css")
knit: (function(inputFile, encoding) { 
      out_dir <- './';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'index.html')) })
editor_options: 
  chunk_output_type: console
---


# Load Packages

```{r}

library(tidyverse) ## Always load tidyverse
library(tidytext) ## Amazing package for all things text analysis
library(tidymodels) ## Modeling framework
library(prodlim) # When prompted with "Do you want to install from sources the package which needs compilation? (Yes/no/cancel)", type "no" and press "Enter"
library(textrecipes) ## Helpful feature engineering for text data
library(rstudioapi) ## set working directory
library(LiblineaR) ## for SVM models
library(ranger) ## for random forest models
library(xgboost) ## for XGBoost models

```


# Load data 

From https://www.kaggle.com/datasets/schmoyote/coffee-reviews-dataset?select=coffee_analysis.csv, I cleaned it up a little bit beforehand 
```{r}

## Set working directory to wherever this script is
setwd(dirname(getActiveDocumentContext()$path))

## Load in csv from that path
coffee <- read.csv("coffee.csv")

```


# Exploring our data

Let's take a look at our data!
```{r, fig.dim = c(11, 7)}

## What's our overall distribution of ratings?
coffee %>%
  ggplot(aes(rating)) +
  geom_histogram(binwidth = 0.999999, color = "black", fill = "#B79990") +
  theme_classic()

## Unnest tokens for plots
tidy_coffee <- coffee %>%
  unnest_tokens(word, review)

## Basic look at most common words
print(tidy_coffee %>%
  count(word, sort = TRUE) %>% 
  slice_head(n = 50))

## On average, which words are used for higher vs. lower scores
tidy_coffee %>%
  ## Group data by word
  group_by(word) %>%  
  ## Count the number of occurrences and average rating associated with each word
  summarise(number_of_uses = n(),
            rating = mean(rating)) %>%
  ## Filter out words that appear fewer than 30 times
  filter(number_of_uses >= 30) %>%
  ## Set up the ggplot with uses on the x-axis and rating on the y-axis
  ggplot(aes(number_of_uses, rating)) +
  ## Add a horizontal line at the overall mean rating
  geom_hline(yintercept = mean(coffee$rating), lty = 2, color = "gray50") +
  ## Add text labels for each word, avoiding overlap
  geom_text(aes(label = word), check_overlap = TRUE, vjust = "top", hjust = "left") +  
  ## Use a logarithmic scale for the x-axis
  scale_x_log10() + 
  ## Yse classic theme
  theme_classic() 

```


# Set up our "data budget" 

A data budget refers to the careful allocation of a dataset into different parts for training, testing, and validation. 
This ensures that the model can be trained and evaluated effectively, preventing overfitting and ensuring that the model generalizes well to unseen data.

Note: we'll use cross-validation folds here, but you could always use `bootstraps()` instead of `vfold_cv()` if you would prefer that approach.
(Uses replacement, good for small datasets)

```{r}

## Set seed for reproducibility
set.seed(123)

## Split data into training and testing sets
## Stratifying by the 'rating' distribution of ratings in both sets
coffee_split <- initial_split(coffee, strata = rating)
coffee_train <- training(coffee_split)
coffee_test <- testing(coffee_split)

## Set another seed for reproducibility (this is what the experts do, idk why)
set.seed(234)
## Create cross-validation folds from the training set for model evaluation
coffee_folds <- vfold_cv(coffee_train, strata = rating)
## View folds
print(coffee_folds)

```


# Set up feature engineering recipes

Feature engineering is the process of creating features (i.e., input variables) for you machine learning model. 
In this context, we are creating features from text data using techniques like tokenization, TF/TF-IDF, and normalization. 
Later on, we'll compare these approaches to see which one performs best.

```{r}

## Recipe 1: tokenizing text and computing TF-IDF features for top 500 words
coffee_rec_tfidf <- 
  recipe(rating ~ review, data = coffee_train) %>%
  step_tokenize(review) %>%
  step_tokenfilter(review, max_tokens = 500) %>%
  step_tfidf(review)

## Recipe 2: tokenizing text and computing TF features for top 500 words
coffee_rec_tf <- 
  recipe(rating ~ review, data = coffee_train) %>%
  step_tokenize(review) %>%
  step_tokenfilter(review, max_tokens = 500) %>%
  step_tf(review)

## Recipe 3: tokenizing text, computing TF-IDF features for top 500 words, 
##  and also removing stopwords and normalizing all predictor variables
coffee_rec_tfidf_stop_norm <- 
  recipe(rating ~ review, data = coffee_train) %>%
  step_tokenize(review) %>%
  step_stopwords(review) %>%
  step_tokenfilter(review, max_tokens = 500) %>%
  step_tfidf(review) %>% 
  step_normalize(all_predictors())


## Check that these steps are working (not required)
prep(coffee_rec_tfidf) %>% bake(new_data = NULL)
prep(coffee_rec_tf) %>% bake(new_data = NULL)
prep(coffee_rec_tfidf_stop_norm) %>% bake(new_data = NULL)

```


# Create some model specifications we want to try

When working with machine learning, you might want to try different types of models to find the one that works best for your specific use case.
Here, we are creating model specifications for three popular algorithms: Linear Support Vector Machine (SVM), Random Forests (RF), and XGBoost (XGB).
Each has its strengths and can be suitable for different types of data and problems!

We are using the "regression" mode for all of these since we are predicting a continuous outcome. 
Many models have a "classification" mode for categorical predictions. 

NOTE: We are going to use all of the defaults for these models. 
In practice, you should absolutely tune important parameters!
For an example, see something like https://juliasilge.com/blog/wind-turbine/

```{r}

## Linear Support Vector Machine is typically a good one for text data
svm_spec <-
  svm_linear() %>%
  set_mode("regression")

## Random forests might be okay given that this dataset involves very short text descriptions
rf_spec <- 
  rand_forest() %>%
  set_mode("regression")

## XGBoost is really popular, so let's give it a try
xgb_spec <-
  boost_tree() %>%
  set_mode("regression")

```


# Put the preprocessing steps and model specification together in a workflow

A workflow helps streamline the process of data preprocessing and model training.
By combining preprocessing steps and model specifications into a single workflow, you can easily manage and compare different models.
Here, we combine multiple preprocessing recipes and model specifications into a workflowset to facilitate easy comparison and evaluation.

```{r}

## Example of setting up an individual workflow
#svm_workflow <- workflow(coffee_rec, svm_spec)

## Set up workflowset (i.e., combining different preprocessing recipes and model specifications)
coffee_models <-
  workflow_set(
    preproc = list(tfidf = coffee_rec_tfidf,                       ## TF-IDF preprocessing recipe
                   tf = coffee_rec_tf,                             ## Term frequency preprocessing recipe
                   tfidf_stop_norm = coffee_rec_tfidf_stop_norm),  ## TF-IDF with stopwords removal and normalization recipe
    models = list(svm = svm_spec,   ## Linear SVM model specification
                  rf = rf_spec,     ## Random Forest model specification
                  xgb = xgb_spec),  ## XGBoost model specification
    cross = TRUE)  ## Cross all preprocessing recipes with all models

## Print the workflow set to check the combinations
coffee_models
```


# Evaluate models

Evaluating different models involves fitting them to the training data and then assessing their performance using our cross-validation folds.
`fit_resamples` trains the model on the training portion of each resample, and evaluates it on the test portion.

```{r}

## Register parallel backend to use multiple processors
doParallel::registerDoParallel()

## Control resamples to save predictions
contrl_preds <- control_resamples(save_pred = TRUE)

## Example of running one model at a time
## Fit the SVM workflow to the resamples
#svm_resamples <- fit_resamples(svm_workflow,
#                               resamples = coffee_folds,
#                               control = contrl_preds)

## Fit all models at once using the workflow set
coffee_resamples <- coffee_models %>%
  workflow_map("fit_resamples",                 ## Specify that we want to fit resamples (cross-validation)
               resamples = coffee_folds,        ## Use the cross-validation folds created earlier
               control = contrl_preds,          ## Control settings for resampling, e.g., save predictions
               metrics = metric_set(rmse, rsq)) ## Specify the metrics to evaluate: Root Mean Squared Error (rmse) and R-squared (rsq)
```


# How do these models compare?

After fitting the models, we compare their performance by collecting metrics, visualizing the results, and ranking the models.
This helps us identify the best model and preprocessing combination for our data.

```{r}

## Collect the metrics for all models
collect_metrics(coffee_resamples)

## Visualize the performance of each model
autoplot(coffee_resamples)

## Rank the models based on Root Mean Squared Error (RMSE)
## This identifies models that minimizes prediction error
rank_results(coffee_resamples, rank_metric = "rmse") 
## Rank the models based on R-squared (R²)
## This identifies models that explain the most variance in the data
rank_results(coffee_resamples, rank_metric = "rsq") 

```


# Final fit 

Let's select the best workflow for reducing error, and make it our final workflow. 
The `last_fit` function fits the final model on the training data and evaluates it on the test data.
You only want to touch the test data once! Only use it when you're really sure.
If the metrics look much worse on your testing data, it's a sign of overfitting to the training data.

```{r}

## Create the final workflow with the best preprocessing recipe and model specification
coffee_finalworkflow <- workflow(coffee_rec_tfidf_stop_norm, svm_spec)

## Fit the final model using the training data and evaluate it on the test data
coffee_finalfitted <- last_fit(coffee_finalworkflow, coffee_split)

## Collect and display the metrics evaluated on the *testing* data
collect_metrics(coffee_finalfitted)

```


# Visualize results 

Extracting the model's coefficients and visualizing the terms with the highest absolute estimates
This helps in understanding which terms (words) are most strongly associated with high or low ratings

```{r, fig.dim = c(8, 8)}

## Extract the final fitted workflow
extract_workflow(coffee_finalfitted) %>%
  ## Convert the model coefficients into a tidy format
  tidy() %>%
  ## Filter out the intercept term
  filter(term != "Bias") %>% 
  ## Group by whether the estimate is positive or negative
  group_by(estimate > 0) %>%
  ## Select the top 15 terms with the highest absolute estimates
  slice_max(abs(estimate), n = 15) %>%
  ungroup() %>%
  ## Clean up the term names by removing the prefix
  mutate(term = str_remove(term, "tfidf_review_")) %>% 
  ## Create a bar plot of the estimates
  ggplot(aes(estimate, fct_reorder(term, estimate), fill = estimate > 0)) +
  geom_col(alpha = 0.8) +
  ## Manually set pretty coffee colors for positive and negative estimates
  scale_fill_manual(values = c("#B79990", "#784F41"), labels = c("low ratings", "high ratings")) +
  ## Add labels and use a classic theme
  labs(y = NULL, fill = "Associated with...") + 
  theme_classic() +
  ## Increase the size of y-axis labels
  theme(axis.text.y = element_text(size = 12))

```

## If I worked for this coffee company, I might recommend avoiding woody notes in the future :)